%-------------------------
% Resume in Latex
% Author : Michael Kennedy
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[pdflang={en-GB}]{hyperref}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage[inline]{enumitem}

\usepackage{pgffor}
\usepackage{needspace}

% fontawesome
\usepackage{fontawesome}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
    \uline{\phantom{#1}}%
    \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style

\renewcommand{\familydefault}{\sfdefault}
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-1pt}}
        }
    }

    %Subheading
    \newcommand{\resumeSubheading}[4]{
        \vspace{-1pt}\item
        \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
            \textbf{\large #1} & {\small #2}\vspace{1pt}\\ % top row of resume entry
            \textit{#3} & {\small #4}\\ % second row of resume entry
        \end{tabular*}\vspace{-4pt}
    }

    %SubSubheading
    \newcommand{\resumeSubSubheading}[2]{
    \item
        \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
            \textit{\small#1} & \textit{\small #2} \\
        \end{tabular*}\vspace{-7pt}
    }

    % Project Heading
    \newcommand{\resumeProjectHeading}[3]{
    \item{
            \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
                \textbf{\large #1} & {\small #3}\vspace{1pt}\\
                \textit{\small#2}\\
        \end{tabular*}
        \vspace{-1em}
    }

}

    \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

    \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

    % CHANGED default leftmargin  0.15 in
    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}
    
    %Contact Item
    \newcommand{\contactinfo}[1]{
        \item[] \small{#1\hspace{1pt}}
    }



\color{text-grey}
\begin{document}
%----------HEADING----------
\begin{center}
\textbf{\Huge{Michael Kennedy}} \\
\vspace{1em}
\begin{itemize*}
    \contactinfo{(831) 917-9737} $|$
    \contactinfo{\href{mailto:michael@michaelkennedy.dev}{michael@michaelkennedy.dev}} $|$
    \contactinfo{\href{https://www.linkedin.com/in/mw-kennedy}{linkedin.com/in/mw-kennedy}} $|$
    \contactinfo{\href{https://github.com/xNS5}{github.com/xNS5}}
\end{itemize*}
\vspace{-1em}
\end{center}


%------------------SUMMARY-----------------------
\section{SUMMARY}
Tenacious and detail-oriented Software Engineer with experience in developing both front-end and back-end applications. Passionate about creating innovative, user-centric solutions. Renowned for excellent communication skills, building strong relationships with stakeholders, and advocating for accessible design. Highlights include developing a scalable PDF tracking solution, an intuitive user-friendly code review application, and an automated website accessibility evaluation utility. Committed to fostering a supportive culture of cross-team collaboration and professional excellence. 

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{Heritage Bank Northwest}{July 2022 -- January 2024}
{Software Developer I}{Burlington, WA}
\resumeItemListStart
\resumeItem{Collaborated with banking analysts to implement features and resolve bugs in Heritage Bank Northwest's banking relationship and treasury management applications.}
\resumeItem{Integrated Bottomline SOAP API to automate onboarding Treasury Management products for customers, eliminating on average 111 clicks per product and reducing the implementation lead time by 50\%.}
\resumeItem{Spearheaded an 80\% reduction in integration time for new services within the Treasury Management application by eliminating hard-coded values and introducing a database-dependent solution.}
\resumeItem{Designed, developed, and tested an interactive application that displays a visual diff of code changes using React.js components to streamline the code review process, enabling both developers and non-developers to quickly identify and review changes made while working on a ticket.}
\resumeItem{Refactored existing REST API in the Java back-end server to improve code quality, and implemented new features to existing API.}
\resumeItemListEnd

\resumeSubheading
{Viking Union (VU), Western Washington University}{June 2019 -- December 2021}
{Computer Maintenance Technician}{Bellingham, WA}
\resumeItemListStart
\resumeItem{Acted as the sole on-site technician providing in-person and remote support during COVID-19 lockdown.}
\resumeItem{Deployed software and hardware to machines and over 50 offices located throughout the Viking Union.}
\resumeItem{Replaced the 3tb shared network drive used by over 200 VU employees with a new 100tb Synology NAS Device.}
\resumeItem{Researched, tested, and deployed a single-application kiosk to the VU information desk using Windows 10, PowerShell, Internet Explorer 11, and local group policy configuration.}
\resumeItem{Created Bash shell scripts to automate the wiping and reformatting of recovered USB drives in the VU’s lost and found.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
     \setlength\itemsep{-0.5em}  
        \item \textbf{General Experience}{: Data Structures, Algorithms, Databases (SQL and NoSQL), Git, CI/CD, Docker, Maven, Azure, SOAP, REST.}
        \item \textbf{Languages}{: Java, Javascript, Typescript, Python, Dart, C\#, Powershell, Bash.} 
        \item \textbf{Frameworks}{: React.js, Node.js, Next.js, Flutter, Django, FastAPI, Flask.}
\end{itemize}



%-----------PROJECTS-----------
\needspace{5in}
\section{PROJECTS}
\resumeSubHeadingListStart 
\resumeProjectHeading{Bellingham Rental Reviews}{Next.js, Typescript, NoSQL, Python, Selenium}{February 2024 -- Present}
    \resumeItemListStart
        \resumeItem{Designed a custom web scraper using Python and Selenium to gather information from Yelp and Google on over 200 property management companies and apartment complexes in the Bellingham, Washington area.}
        \resumeItem{Extracted and transformed data into JSON format, and adjusting review metrics for clarity and consistency.}
        \resumeItem{Utilized OpenAI to analyze JSON data and generate markdown articles for each entity, enriching data insights and presentation.}
        \resumeItem{Wrote documentation to outline the purpose of the project, as well as technical information on the scripts used to gather data.}
        \resumeItem{Created an accessible website using Next.js to showcase AI-generated reviews, stored in Firebase NoSQL database.}
    \resumeItemListEnd

    \resumeProjectHeading{Accessibility Testing Automation Application}{Sails.js, Vue.js, Selenium, Python, Deque aXe API}{July 2021 -- January 2022}
    \resumeItemListStart
        \resumeItem{Led a team of 4 in the development of a full-stack accessibility checking application for Wandke Consulting -- an accessibility consulting company in Bellingham, WA.}
        \resumeItem{Facilitated code reviews for new features and gave feedback to team members.}
        \resumeItem{Utilized Deque Labs’ aXe accessibility API and Selenium Webdriver to scan websites and test for over 350 Web Content Accessibility Guideline (WCAG) violations.}
        \resumeItem{Implemented REST API routes in the Sails.js backend and integrated a custom Python web crawler.}
    \resumeItemListEnd

    \resumeProjectHeading{Web Content Accessibility Guideline (WCAG) Reference CJS}{Javascript}{July 2021 - January 2022}
        \resumeItemListStart
            \resumeItem{Forked and modified the NodeJS Package "WCAG Reference" to work as a CommonJS import.}
            \resumeItem{Created a function to locate and return all WCAG success criterion of a given level (A-AAA).}
            \resumeItem{Upgraded the WCAG scrapers to include short and long descriptions of WCAG guidelines in the JSON output.}
            \resumeItem{Utilized Github Actions to deploy updates to Npmjs.com.}
          \resumeItemListEnd

          \resumeProjectHeading{ReLeave}{Flutter, SQLite}{January 2021 - March 2021}  
    \resumeItemListStart
        \resumeItem{Led a team of 4 in the development of a cross-platform mobile application to assist people going through cannabis use disorder recovery.}
        \resumeItem{Conducted research, and interviewed Substance Use Disorder specialists with Sea-Mar Community Health Centers to develop a list of functional requirements.}
        \resumeItem{Integrated Reddit API using the Dart Reddit API Wrapper (DRAW) to interact with over 200,000 users on the /r/Leaves subreddit.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading{Western Washington University (WWU)}{}
{Bachelor of Science in Computer Science, Minor in Communication Studies}{Bellingham, WA} 
\resumeSubHeadingListEnd


\end{document}
